---
title: "Lab 5"
author: "Marco Palombo"
date: "10/26/2021"
output: 
  html_document: 
    toc: yes
    theme: cosmo
    number_sections: yes
    code_folding: hide
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```
# Confidence Intervals

In this section we'll learn to use the `t.test()` function as a way to return the confidence intervals using the t-distribution. 

## Example 1

Crete a mock sample of observation values and find the confidence interval. The we'll learn how to report that.

```{r}
pika_mass <- c(82, 94, 110, 70, 86, 99, 102)

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)

pika_ci
```

## Risky and tedious way:

Mean pika mass at Paiute Pass is 91.9 g $\pm$ (mean $\pm$ 1 standard deviation, n = 7) with a 95% confidence interval of [79.4, 104.4] g

### A high initial investment, but safer and better way

In-line code referencing to stored objects!

Use a single backtick on either side of a lowercase r to create an in-line bit of code.

Mean pika mass t Paiute Pass is `r round(pika_mean, 1)` g $\pm$ `r round(pika_sd, 1)`g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r round(pika_ci$conf.int[1],1)`, `r round(pika_ci$conf.int[2],1)`]

# Two-sample t test

Use a two-sample t-test to test the null hypothesis tht samples were drawn from populations with the same mean (difference is means = 0). 

- H0: means difference = 0
- HA: Means difference is not= 0

This is a two-sided t-test becasue no directionality is implied

## /Example 1

```{r}
oak_trees <- c(29, 18, 19, 22, 30, 19, 18, 7)
pine_trees <- c(48, 52, 46, 70, 58,48, 59, 69)


```

Is there a significant difference in mean heights for oak and pine trees?

```{r}
trees_t <- t.test(oak_trees, pine_trees)
```

The p-value of `r trees_t$p.value` means that there is a `r 100 * trees_t$p.value` % chance of finding sample means at least as different as those I found by random chance if they were drawn from populations with the same mean height.

